A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-09-01 docs/data_v1.01.tex
Revistied most of the lensing section.

>>>>

\paragraph{HST imaging.} [TO DO] Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed \citep{SWELLSI}). The WF3 CCD chip pf WFPC2. The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec. Filters F450W and F814W. Redshifts Lens image redshift $z_s = 0.254$  \citep{SWELLSIII} This galaxy is at a redshift of $z_d = 0.113$ (\cite{SWELLSIII}). Angular diameter distance according to [TO DO: REF: Dunkley] is 414 Mpc, which translates into a scaling of 1 arcsec $\hat{=}$ 2.01 kpc for J1331.

### 2015-09-01 docs/introduction_v1.01.tex
Revistied most of the lensing section.

\paragraph{SWELLS Survey}
\begin{itemize}
\item [TO DO]
\item \citet{SWELLSI} give measurements for the apparent AB magnitudes for the HST/WFPC2 I-band/F814W filter for disk and bulge, as well as stellar masses for stellar population models for a Chabrier [TO DO: REF] and Salpeter [TO DO: REF] initial mass function (IMF). 
\end{itemize}

\paragraph{Characteristics of J1331}
\begin{itemize}
\item SDSS J1331+3638 (J1331)
\item approximate hubble type Sb
\item first discovered by Sloan digital sky survey (SDSS) [TO DO: REF]
\item at redshift $z_d\simeq0.113$ [TO DO: REF]
\item \citet{SWELLSI} identified it as a strong lens
\item large reddish bulge and bluish spiral arms, see Fig. \ref{fig:F450W} and \ref{fig:F814W}
\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see Fig. \ref{fig:lens_just_imgpos}
\item lensed object might be a star-forming blob of a background galaxy.
\item Lensing properties first analysed by \citet{SWELLSIII}
\item rather edge-on $\longrightarrow$ possible to measure rotation curves. \citet{SWELLSV} measured the gas and stellar rotation curves along the major axis. Fitted galaxy model to gas kinematics at large radii, and lensing result
\item large counter-rotating core, see Fig. \ref{fig:kinematics}
\item possible minor merger in the past
\end{itemize}

>>>>

\paragraph{SWELLS Survey}
\begin{itemize}
\item [TO DO]
\item Sloan WFC Edge-on Late-type Lens Survey (SWELLS) WFC = Wide field camera \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI}
\item \citet{SWELLSI} give measurements for the apparent AB magnitudes for the HST/WFPC2 I-band/F814W filter for disk and bulge, as well as stellar masses for stellar population models for a Chabrier [TO DO: REF] and Salpeter [TO DO: REF] initial mass function (IMF). 
\item dedicated to find spiral galaxy strong lenses, to combine lensing and dznamical modelling to break degeneracies inherent in both methods.
\item picked galaxies in SDSS whose spectra had to different redshifts within 3 arcsec, which makes it likely to capture strong lenses with typical Einstein radii of 1 arcsec. Sufficiently inclined galaxies were picked by eye. Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed \citep{SWELLSI}).
\end{itemize}

\paragraph{Characteristics of J1331}
\begin{itemize}
\item SDSS J1331+3638 (J1331)
\item approximate hubble type Sb, Spiral galaxy almost edge-on
\item first discovered by Sloan digital sky survey (SDSS) [TO DO: REF]
\item \citet{SWELLSI} identified it as a strong lens
\item Its coordinates on the sky are right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). 
\item This galaxy is at a redshift of $z_d = 0.113$ (\cite{SWELLSIII}).
\item large reddish bulge and bluish spiral arms, see Fig. \ref{fig:F450W} and \ref{fig:F814W}
\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see Fig. \ref{fig:lens_just_imgpos}, approximately at a distance of 1 arcsec from the galaxy center (which is a typical Einstein radius).
\item Lens image redshift $z_s = 0.254$  \citep{SWELLSIII}
\item lensed object might be a star-forming blob of a background galaxy.
\item Lensing properties first analysed by \citet{SWELLSIII}
\item rather edge-on $\longrightarrow$ possible to measure rotation curves. \citet{SWELLSV} measured the gas and stellar rotation curves along the major axis. Fitted galaxy model to gas kinematics at large radii, and lensing result
\item large counter-rotating core, see Fig. \ref{fig:kinematics}
\item possible minor merger in the past
\item background object: possibly bright star forming region in the spiral arms of background galaxy 
\end{itemize}

### 2015-09-01 docs/model_lensing_v1.02.tex
Revistied most of the lensing section.

\subsection{Strong Gravitational Lensing Formalism and Lens Model}

\paragraph{Lensing Formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
\begin{equation}
\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
\end{equation}
where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
\begin{equation}
\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vec{\theta}_i = (x_i,y_i)$. The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
\end{equation}
\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
\\The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
Lines in the image plane for which the magnification becomes infinite, i.e. $\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}. The corresponding lines in the source plane are called \emph{caustics}. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
\begin{equation*}
M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation*}
where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.

\paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
\begin{equation*}
\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
\end{equation*}
for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky. The case $\alpha = 1$ corresponds to a flat rotation curve. We expand $F(\theta)$ into a Fourier series,
\begin{equation}
F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
\end{equation}
For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
\begin{equation}
\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
\end{equation}
\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$. When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.

\paragraph{Model fitting.} As described above our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq. (\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}). We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$. Because we want to avoid solving the lens equation (cf. eq. (\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq. (\ref{eq:magnificationtensor}):
\begin{eqnarray*}
\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
\end{eqnarray*}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation*}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
\end{equation*}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation*}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
\end{equation*}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}. But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting. Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab. \ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve. In the following we therefore set $\alpha=1$.

>>>>

\subsection{Strong Gravitational Lensing Formalism and Lens Model} \label{sec:lensing_theo}

\paragraph{Lensing Formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
\begin{equation}
\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
\end{equation}
where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$\footnote{$\xi$ and $\eta$ are cartesian coordinates on the plane of the sky.} is deflected according to the lens equation
\begin{equation}
\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vec{\theta}_i = (x_i,y_i)$. The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
\end{equation}
\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
\\The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
Lines in the image plane for which the magnification becomes infinite, i.e. $\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}. The corresponding lines in the source plane are called \emph{caustics}. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
\begin{equation*}
M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation*}
where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.

\paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
\begin{equation}
\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
\end{equation}
for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky. The case $\alpha = 1$ corresponds to a flat rotation curve. We expand $F(\theta)$ into a Fourier series,
\begin{equation}
F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
\end{equation}
For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
\begin{equation}
\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
\end{equation}
\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$. When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.

\paragraph{Model fitting.} As described above our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq. (\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}). We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$. Because we want to avoid solving the lens equation (cf. eq. (\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq. (\ref{eq:magnificationtensor}) to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $ and the $\chi^2_\text{lens}$ that the fit wants to minimize becomes
\begin{eqnarray*}
\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
\end{eqnarray*}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at $\vec{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation*}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
\end{equation*}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation*}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
\end{equation*}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}. But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction make flux determination too unreliable and we do not include them in the fitting.

[TO DO: eq. to Equation, fig. to Figure, \S to Section, vec to vect, cf to see, tab. to Table]

### 2015-09-01 docs/results_lensing_v1.02.tex
Revistied most of the lensing section.

\subsection{Mass distribution from Lensing}

\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits (cf. \S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in tab. \ref{tab:MGEF814W} convolved with the PSF in tab. \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig. \ref{fig:lens_just_imgpos}). Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in tab. \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.

@@

\paragraph{Best fit lens model.} The best fit lens model for the image positions in tab. \ref{tab:lenspos} is given in the first column of tab. \ref{tab:bestfitlensmodel}. Fig. \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model. Fig. \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F814W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab. \ref{tab:lenspos} and a standard deviation corresponding to the measurement error of 1 pixel. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab. \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec. The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{??? Critical curves, Einstein radius, caustics, source position for best fit model. ??? [TO DO: nice caption]}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{??? Time delay surface ??? [TO DO: nice caption]}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{???}
\label{fig:???}
\end{figure*}

>>>>

\subsection{Mass distribution from Lensing} \label{sec:results_lensing}

\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in tab. \ref{tab:MGEF814W} convolved with the PSF in tab. \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig. \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF. Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in tab. \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions. We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in tab. \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

@@

\paragraph{Best fit lens model.} The best fit lens model for the image positions in tab. \ref{tab:lenspos} is given in the first column of tab. \ref{tab:bestfitlensmodel}. Fig. \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. This cricital curve is called \emph{tangential}, because of the tangential orientation of the images close to it. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. This is a good indication that indeed all four images are indeed lensing images of the same object. Fig. \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab. \ref{tab:lenspos} and a standard deviation corresponding to the measurement error. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab. \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius). The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{Best fit critical curve, Einstein radius, caustic, source position.}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{Time delay surface.}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an Iraf Ellipse model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size. The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots. The Einstein radius of the best fit lens model is shown as a red dotted circle. \emph{Panel (a)} Besides the image positions and Einstein radius, the critical curve (red solid line) is shown in the lens plane. The caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are both located in the source plane, are shown as well. For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model. \emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \ref{eq:timedelay} of the best fit lens model. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis. The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well. [TO DO: Add A, B, C, D in the figure to make clear which image is which.]}
\label{fig:???}
\end{figure*}
